Think deep for reef resilience

### 2025-08-14 paper/paper_draft.qmd
Adjust wording when talking about deployment considerations

Current reef restoration and intervention-investigation efforts on the GBR, such as
deployment of coral seeding and fragment devices, target reefs with suitable restoration
sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. One of the main
constraints on deployment depth is visual identification of target sites from the surface
for deployment and ongoing monitoring, in combination with factors such as deployment method
and tourism return value. Our results suggest that of the assessed reefs ocurring within the
1-10m depth range (1736 reefs), 62% (1082) of reefs fall into the low and medium clusters
(across all GCMs at the GBRMPA management region scale), with many unable to maintain
positive carbonate budgets under future conditions. Reef intervention planning is a complex
and challenging decision making process [@anthony2020], and our results suggest that
deployment site depth is an important factor to consider when assessing the long-term
resilience of deployment sites.

>>>>

Current reef restoration and intervention-investigation efforts on the GBR, such as
deployment of coral seeding and fragment devices, target reefs with suitable restoration
sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. One of the main
constraints on deployment depth is visual identification of target sites from the surface
for deployment and ongoing monitoring, in combination with factors such as deployment method
and tourism return value. Our results suggest that of the assessed reefs ocurring within the
1-10m depth range (1736 reefs), 62% (1082) of reefs fall into the low and medium clusters
(across all GCMs at the GBRMPA management region scale), with many unable to maintain
positive carbonate budgets under future conditions. Reef intervention planning is a complex
and challenging decision making process [@anthony2020], and our results suggest that
deployment site depth may be an important factor to additionally consider when assessing the long-term
resilience of deployment sites.
